\chapter{Project and Its Background}

\section{Project Context}

Cheating is acting dishonestly or unfairly to gain an advantage according to Oxford English Dictionary.
This is commonly happening during examinations and is not a new problem of every educational institution.

The examination is a formal test that is taken to show the knowledge or ability in a particular subject or to obtain a qualification according to Collins Dictionary.
Schools and colleges must assess students.
However, examinations are putting too much pressure on students as the examination results will greatly affect their school performance and future careers.
For this primary reason, students cheat.

Cheating in exams compromises the standard of education in the country and negatively affects the ability of the students to compete on the world stage.
Students who cheat become poor decision-makers in their careers.
Their productivity and level of integrity are adversely dented by their belief in having everything the easy way.

For this reason, educational institutions are promoting academic integrity by setting up rules and regulations and supervising students during examinations.
The presence of an instructor during examinations minimizes the chances of student misbehavior.
This is expectedly efficient in the regular classes but most likely not in Online/distance learning.

Online/distance learning is the acquisition of knowledge that takes place through electronic technologies and media \cite{abernathy2020elearning}.
It is an increasingly popular method of receiving higher education, often serving an off-campus population who cannot attend class on campus \cite{daffin2018comparing}.
Accordingly, e-learning is conducted on the Internet, where students can access their learning materials online at any place and at any time.

The development of multimedia and information technologies, as well as the use internet as a new technique of teaching, has made radical changes in the traditional process of teaching \cite{liu2009comparative}.
This negatively impacts the traditional prevention of cheating, because of the lack of presence of instructors during examinations.
\citeA{berkey2015cheating} have examined the sensitive subject of cheating in online courses and found an alarming 84 of 141 students who responded to their survey agreed that student dishonesty in online test-taking was a significant issue.

The major way of coping with academic dishonesty is the adoption of an online proctoring system for online assessments.
Online proctoring systems combat academic dishonesty as it produces a secure solution in monitoring test takers.

Numerous online proctoring services are appearing on the market that portend to offer test integrity.
However, there are instances that they are remained untried and untested mainly because of the cost of service and their technical requirements.
Privacy protection and management, security, and anti-fraud measures are also other key issues that need to be examined when considering an online proctoring system \cite{sietses2016white}.

\section{Purpose and Description}

Due to the COVID 19 Pandemic where onsite teaching is temporarily ceased, AMA Computer College Parañaque implements full distance learning before blended learning to continue providing education to students.
It is a full online learning platform where the results in every online assessment of every course sum the performance or academic grade of the students.

This profound a convenient way of receiving a college degree, students should just have to study online and pass the assessment.
However, there is a gap.
AMA Computer College Parañaque is still conducting unproctored online examinations, a type of examination that is unsupervised and can be taken without a teacher or "proctor" present, which is prone to academic dishonesty.

It is very common for students to cheat in unproctored online exams as it gives them the full and free utilization of the internet to ace their scores.
Due to this, when comparing the scores to the proctored online courses or the traditional classroom, scores are significantly higher \cite{weiner2017comparative}.
However, the results are considered inconsequential as it has no impact on student's educational growth.

AMA Computer College Parañaque online examinations experience multiple challenges coexisting due to its examination being unproctored.
First, students can leave the exam to look for answers on the websites that are buying answer keys to students like Course Hero and to ask someone who has finished the exam for answers.

Second, no student authentication.
There is no guarantee that the enrolled student that owns the account is the one taking the exam.
There are a lot of cases where students pay for someone to take the exam for them.

These are serious issues for academic integrity and distance learning credibility that can be thoroughly prevented using a proctor who can spot students' malpractices.
Otherwise, having no one to look out for encourages students to continue cheating practices \cite{teh2013reducing}.

Having considered the above issues and concerns, the researchers were motivated to propose a web-based Automated online examination proctor for AMA Computer College Parañaque.
This is an innovation of the current Online Assessment that promotes a fair online examination by recognizing the true examinee, detecting students who are leaving the exam, and shutting down exams when students receive multiple violations.

\section{Objective of the Study}
This research aims to develop an Automated Online Examination Proctor for AMA Computer College Parañaque and to attain the following:
\begin{enumerate}
   \item Identify the different malpractices that are conducted during online examinations.
   \item Design and create a web-based Online Examination Proctor to eliminate cheating activities during the online examination.
   \item Assess the effectiveness and usability of the web-based Automated Online Examination Proctor.
\end{enumerate}

\section{Significance of the Study}

Proctor Vue: Automated Online Examination proctor is undertaken with the main purpose of detecting and preventing student's malpractices during the online examination to attain academic integrity in the online learning environment of AMA Computer College Parañaque.
This program generously benefits the students, professor, or teaching assistants, the AMA Computer College Parañaque, the proponents, and the future researchers.

\textbf{Students} - The effectiveness of the system will benefit them as practicing online exam integrity and minimizing cheating dependency would maximize their opportunity to learn, productivity, develop and improve skills, and obtain an educational degree that reflects their academic achievements.

\textbf{Professor or teaching assistants} - The system is important to the faculty members, since it will provide them the fairly evaluated student's performance.
With this, Professor or teaching assistants would be able to track student's difficulties, and check for any improvements of the online courses or assessments.

\textbf{Proponents} - The effectiveness of the system will provide the administration a fair distance learning environment that would produce graduates whom is practiced with academic integrity.

\textbf{Future Researchers} - The proposed study can serve as a reference to future researchers who aims to combat academic dishonesty in the online learning platform.

\section{Scope and Limitation}

The proposed system is designed for AMA Computer College Parañaque examination faculty and enrolled students qualified for assessments of online courses.
It provides features of face recognition, detection of tab switching, and shutdown for the online examinations that type is limited to Multiple choice, Matching type, and True/False test and these are the current types of examination the AMA Computer College Parañaque is implementing.

Further, the proposed system is an Automated online proctoring that is a relatively new technology that uses the student's webcam empowered by artificial intelligence to verify student and student's behavior.
Therefore, proctor nor a licensed online proctor is no longer needed in facilitating examinations.

The study focuses on the effectiveness of the system for the students who are currently enrolled in the fully online learning platform of AMA computer college Parañaque.

\section{Definition of Terms}

\textbf{Amazon Elastic Compute Cloud}.
It is a web service that provides secure and scalable compute capacity in the cloud.

\textbf{Amazon Simple Storage Service}.
It is an object storage service that offers industry-leading scalability, data availability, security, and performance.

\textbf{Amazon Web Services}.
It is a subsidiary of Amazon providing on-demand cloud computing platforms and APIs to individuals, companies, and governments, on a metered pay-as-you-go basis.

\textbf{Application Programming Interface}.
It is a software that allows two applications to communicate to each other.

\textbf{Back end}.
It is the part of a computer system or application that is not directly accessed by the user, typically responsible for storing and manipulating data.

\textbf{Browser}.
It is a computer program with a graphical user interface for displaying and navigating between web pages.

\textbf{Computer ethics course}.
This course is intended to give students a chance to reflect on the humanitarian, social, and professional impact of computer technology by focusing on ethical issues faced by and brought about by computing professionals

\textbf{End–user}.
The person who actually uses a particular product.

\textbf{Front end}.
It is a software program or website where the user interacts. It is similar to user interface.

\textbf{Intellectual network}.
It is about presupposing a group of people who maintain continuous ties and participate in common educational, political or cultural projects, within civil society and even beyond its walls, whether in or outside the nation state.

\textbf{Internet site}.
A website or a webpage containing different contents.

\textbf{JavaScript}.
It is an object-oriented computer programming language commonly used to create interactive effects within web browsers.

\textbf{Server Side}.
It is the action takes place on a web server.

\textbf{Static content}.
It is any content that can be delivered to an end user without having to be generated, modified, or processed.

\textbf{Surfing the internet}.
It is the browsing of websites in the internet

\textbf{Unproctored assessments}.
These are unsupervised tests that can be taken without a teacher or "proctor" present.

\textbf{Web application}.
An application software that runs on a web server, unlike computer-based software programs that are run locally on the operating system (OS) of the device.

\textbf{Web server}.
a computer that runs websites. It's a computer program that distributes web pages as they are requisitioned.
